VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-01-31 snapshot_system/paper_conc.tex
rev

\section{Conclusion}
\label{sect:conclusion}
%In this paper we propose a collocated backup service built on
%the top of a cloud cluster to reduce network traffic and infrastructure requirements.
The main contribution of this paper is a low-profile and VM-centric deduplication scheme to 
maximize fault isolation while delivering competitive deduplication efficiency using
a small amount of system resource.
Evaluation using  this scheme strikes a tradeoff and restricted cross-VM duplicate detection
can accomplish up to 96.58\% of what complete global
deduplication can do, and the approximate snapshot deletion effectively manages deleted chunks with a 
low-resource usage.  The availability of snapshots increases substantially when
adding more replication for popular cross-VM chunks and packaging chunks from the same 
VM in one file system block. The analysis shows that the replication degree
for the popular data set between 6 and 9 is good enough when the replication degree
for other data blocks is 3.
%Currently we are studying how the

>>>>

\section{Conclusion}
\label{sect:conclusion}
%In this paper we propose a collocated backup service built on
%the top of a cloud cluster to reduce network traffic and infrastructure requirements.
The main contribution of this paper is a low-profile and VM-centric deduplication scheme to 
maximize fault isolation while delivering competitive deduplication efficiency using
a small amount of system resource.
Evaluation using  this scheme strikes a tradeoff and restricted cross-VM duplicate detection
can accomplish up to 96.58\% of what complete global
deduplication can do, and the simple and approximate snapshot deletion 
effectively manages deleted chunks with a 
much lower resource usage.  The availability of snapshots increases substantially when
adding more replication for popular cross-VM chunks and packaging chunks from the same 
VM in one file system block. The analysis shows that the replication degree
for the popular data set between 6 and 9 is good enough when the replication degree
for other data blocks is 3.
%Currently we are studying how the

### 2014-01-31 snapshot_system/paper_eval.tex
rev

The space cost for deletion and leakage repair is very small.
Consider each reference consumes 8 bytes plus  1 mark bit. 
A VM that has 40GB backup data with about 10 million chunks will need less than 85MB of memory.
A VM-specific mark-and-sweep process takes  less than half an hour, when disk bandwidth is controlled as 50MB/s.

When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, a total of 212GB memory
space on 100 node is accessed for processing each VM and each machine quires 2.12GB.
Assuming snapshot deletion happens daily,
such a  mark-and-sweep deletion needs to be conducted every two days to control garbage space under 5\%
since there is 2.5\% data change for each snapshot.

>>>>

The space cost for deletion is insignificant.
Leakage repair need less than 85MB of memory
considering each reference consumes 8 bytes plus  1 mark bit and  
each VM snapshot has 40GB backup data with about 10 million chunks. 
Our VM-specific mark-and-sweep process in VC takes  less than half an hour, when disk bandwidth is controlled as 50MB/s. 
When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, 
a total of 212GB memory
space on 100 node is accessed for processing each VM and each machine requires 2.12GB.
To control the garbage growth, such a process needs to be conducted much more frequently than our
VM-centric leakage repair. 
%Assuming snapshot deletion happens daily,
%such a  mark-and-sweep deletion needs to be conducted every two days to control garbage space under 5\%
%since there is 2.5\% data change for each snapshot.
